Individual and Differential Harm in Redistricting

### 2025-04-28 paper/harm-short.Rmd

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Anonymous Authors
abstract: |
  Social scientists have developed dozens of measures for assessing partisan bias in redistricting.
  But these measures are not easily adapted to other groups, 
  including groups defined by race, class, or geography.
  Nor are they applicable to single- or no-party contexts, such as local redistricting.
  To overcome these limitations, we propose a unified framework of harm for evaluating 
  the impacts of a districting plan on individual voters and the groups to which they belong. 
  We consider a voter harmed if their chosen candidate is not elected under the current plan, 
  but would be under a different plan.
  Harm improves on existing measures by both focusing on the choices of individual voters 
  and directly incorporating counterfactual plans.
  We discuss strategies for estimating harm, and demonstrate the utility of our framework 
  through analyses of partisan gerrymandering in New Jersey and voting rights 
  litigation in Alabama.
keywords:
  - representation
  - redistricting
  - voting rights
  - individual harm
bibliography: references.bib
biblio-style: apsr
fontsize: 12pt
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options:
  markdown:
    wrap: sentence
---

>>>>

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Anonymous Authors
abstract: |
  Social scientists have developed dozens of measures for assessing partisan bias in redistricting.
  But these measures are not easily adapted to other groups, 
  including groups defined by race, class, or geography.
  Nor are they applicable to single- or no-party contexts, such as local redistricting.
  To overcome these limitations, we propose a unified framework of harm for evaluating 
  the impacts of a districting plan on individual voters and the groups to which they belong. 
  We consider a voter harmed if their chosen candidate is not elected under the current plan, 
  but would be under a different plan.
  Harm improves on existing measures by both focusing on the choices of individual voters 
  and directly incorporating counterfactual plans.
  We discuss strategies for estimating harm, and demonstrate the utility of our framework 
  through analyses of partisan gerrymandering in New Jersey and voting rights 
  litigation in Alabama.
keywords:
  - representation
  - redistricting
  - voting rights
  - individual harm
bibliography: references.bib
biblio-style: apsr
citeproc: false
fontsize: 12pt
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options:
  markdown:
    wrap: sentence
---
